---
title: "ADHOC"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(ggplot2)
```

##1

Create a getNodes function which generates random Nodes.

```{r}
getNodes = function(n){
# n is numeric singleton vector
# Nodes is a matrix with n by 2
  
  Nodes = matrix(runif(2*n,0,100), ncol = 2)
  colnames(Nodes) <- c("x","y")
  rownames(Nodes) <- 1:n
  
  return(Nodes)
}
```

Check the getNodes function with random values

```{r}

seeds = vector(length = 5, mode = "list")
set.seed(12345678)

test.node = list()

for (i in 1:5){
  seeds[[i]] = .Random.seed
  node = getNodes(5)
  test.node[[i]] = node
}

test.node

```

##2
Find the smallest radius Rc.
First, Set up a helper function, findTranMat, to find a transition Matrix(Marcov Matrix for random walk).

```{r}

findTranMat = function(mat, R){
  trans.mat = as.matrix(mat)
  trans.mat[trans.mat <= R] = NA
  trans.mat[trans.mat > R] = 0
  trans.mat[is.na(trans.mat)] = 1
  trans.mat = apply(trans.mat, 1, "/", rowSums(trans.mat))
  return(trans.mat)
}

```

Second, find a second largest eigen values since the largest eigen value gives us the trivial solution as well. Set up a helper function, genEigen2() which finds a second largest eigen value.

```{r}

getEigen2 = function(mat){ 
  eigenvalues = eigen(mat)$values
  SecondLargest = sort(eigenvalues, decreasing = TRUE)[2]
  return(Mod(SecondLargest))
}

```

Third, set up a function findRange() to find the range of Rc

```{r}

findRange = function(mat){
  Mini = min(mat)
  Maxi = max(mat)
  Min.Max = c(Mini, Maxi)
  names(Min.Max) = c("Lower Bound","Upper Bound")
  return(Min.Max)
}

```

Set up a function, findRc, to find the smallest radius to make the network fully connected

```{r}

findRc = function(nodes, tol = 0.05){
  mat = dist(nodes)
  lower = findRange(mat)[1]
  upper = findRange(mat)[2]
  midpt = sum(upper, lower) / 2

  while(upper-lower > tol){
    TranMat = findTranMat(mat, midpt)
    EigenValue = round(getEigen2(TranMat), digits = 5)
    if(EigenValue < 1){
      upper = midpt
    }else{
      lower = midpt
    }
    midpt = sum(upper, lower) / 2
  }
  names(upper) = "The smallest Radius"
  return(upper)
}

```


Check the findRc function with random Node

```{r}

nodes = getNodes(100)
findRc(nodes)

```

##3

Generate 1000 networks and for each find the value for Rc. Examine the distribution of these Rc values.

sample with size n = 20, n = 50, n = 100

```{r}

Rc1 = c()
Rc2 = c()
Rc3 = c()

seeds = vector(length = 2, mode = "list")
set.seed(12345678)

n1 = 20
n2 = 50
n3 = 100

networks1 = vector("list",1000)
networks2 = vector("list",1000)
networks3 = vector("list",1000)

for(i in 1:1000){
  seeds[[i]] = .Random.seed
  networks1[[i]] = getNodes(n1)
  networks2[[i]] = getNodes(n2)
  networks3[[i]] = getNodes(n3)
}



networks = list(networks1, networks2, networks3)

for(i in 1:1000){
  Rc1[i] = findRc(networks1[[i]])
  Rc2[i] = findRc(networks2[[i]])
  Rc3[i] = findRc(networks3[[i]])
}

Rc = list(Rc1, Rc2, Rc3)

```

As n goes up, the radius of the Rc is getter smaller.
Set up a function to visualize the distribution of Rcs.

```{r}

plotRc = function(Rc1, Rc2 = NULL, Rc3 = NULL, bw = 2, title = 'Compare Rc with different size'){
  Rcs = data.frame(Rc123 = c(Rc1, Rc2, Rc3), 
                   strat = rep(c(1,2,3), times = c(length(Rc1), length(Rc2), length(Rc3))))
  ggplot(data = Rcs) + 
    geom_density(aes(x = Rc123, y = ..density.., color = factor(strat)), bw = bw) +
    scale_x_continuous("Smallest Radius(Rc) for 1000 Networks") +
    ggtitle(title) +
    scale_colour_manual(values = c(1,2,3), name = 'Density', labels = c('Rc1','Rc2','Rc3'))
}

```

Plot distribution of Rcs.

```{r}

plotRc(Rc1, Rc2, Rc3, title = "Compare Rc for 1000 networks with different size\nRc1 with size of 20, Rc2 with size of 50, Rc3 with size of 100")

```

Plot Histogram of Rcs with summary.

```{r}

Rc = list(Rc1, Rc2, Rc3)
Hist1 = hist(Rc1, breaks = 20, col = "pink", 
             xlab = "Rc of 1000 networks with size 20", 
             main = "Histogram of Rc of 1000 Networks")
Hist1
Hist2 = hist(Rc2, breaks = 20, col = "blue", 
             xlab = "Rc of 1000 networks with size 50", 
             main = "Histogram of Rc of 1000 Networks")
Hist2
Hist3 = hist(Rc3, breaks = 20, col = "green", 
             xlab = "Rc of 1000 networks with size 100", 
             main = "Histogram of Rc of 1000 Networks")
Hist3
     
```

Set up min, median, mean, and max values for Rc

```{r}

Min = c()
Median = c()
Mean = c()
Max = c()

for (i in 1:3){
  Min[i] = min(Rc[[i]])
  Median[i] = median(Rc[[i]])
  Mean[i] = mean(Rc[[i]])
  Max[i] = max(Rc[[i]])
}

i = c()
j = c()
k = c()
l = c()

for (h in 1:3){
  i[h] = which(abs(Rc[[h]] - Min[h]) == min(abs(Rc[[h]] - Min[h])))[1]
  j[h] = which(abs(Rc[[h]] - Median[h]) == min(abs(Rc[[h]] - Median[h])))[1]
  k[h] = which(abs(Rc[[h]] - Mean[h]) == min(abs(Rc[[h]] - Mean[h])))[1]
  l[h] = which(abs(Rc[[h]] - Max[h]) == min(abs(Rc[[h]] - Max[h])))[1]
}

```

##4
Plots of Rc with the four values(min, median, mean, max)

Plots of Rc with the min
```{r}

mindf = list()
connected = list()
connections = list()

for (h in 1:3){
  mindf[[h]] = data.frame(networks[[h]][i[h]])
  comb = combn(nrow(mindf[[h]]), 2)
  connected[[h]] = comb[,which(as.numeric(dist(data.frame(networks[[h]][i[h]])))<=Rc[[h]][i[h]])]
  connections[[h]] = data.frame(
    from = mindf[[h]][connected[[h]][1, ], 1:2],
    to = mindf[[h]][connected[[h]][2, ], 1:2]
    )
  names(connections[[h]]) = c("x1", "y1", "x2", "y2")
}

color = c("pink", "blue", "green")
title = c("Plots of the Min Rc with size of 20", "Plots of the Min Rc with size of 50", "Plots of the Min Rc with size of 100")

for (h in 1:3){
  plot = 
    ggplot(mindf[[h]], aes(x = mindf[[h]]$x, y = mindf[[h]]$y)) + 
    geom_point(col = "black", size = 3) +
    geom_segment(data = connections[[h]], 
                 aes(x = x1, y = y1, xend = x2, yend = y2), col = color[h]) +
    labs(x = "X-coordinate", y = "Y-coordinate", title = title[h])
  print(plot)
}


```

Plots of Rc with the median

```{r}

mindf = list()
connected = list()
connections = list()

for (h in 1:3){
  mindf[[h]] = data.frame(networks[[h]][j[h]])
  comb = combn(nrow(mindf[[h]]), 2)
  connected[[h]] = comb[,which(as.numeric(dist(data.frame(networks[[h]][j[h]])))<=Rc[[h]][j[h]])]
  connections[[h]] = data.frame(
    from = mindf[[h]][connected[[h]][1, ], 1:2],
    to = mindf[[h]][connected[[h]][2, ], 1:2]
    )
  names(connections[[h]]) = c("x1", "y1", "x2", "y2")
}

color = c("pink", "blue", "green")
title = c("Plots of the Median Rc with size of 20", "Plots of the Median Rc with size of 50", "Plots of the Median Rc with size of 100")

for (h in 1:3){
  plot = 
    ggplot(mindf[[h]], aes(x = mindf[[h]]$x, y = mindf[[h]]$y)) + 
    geom_point(col = "black", size = 3) +
    geom_segment(data = connections[[h]], 
                 aes(x = x1, y = y1, xend = x2, yend = y2), col = color[h]) +
    labs(x = "X-coordinate", y = "Y-coordinate", title = title[h])
  print(plot)
}


```

Plots of Rc with mean

```{r}

mindf = list()
connected = list()
connections = list()

for (h in 1:3){
  mindf[[h]] = data.frame(networks[[h]][k[h]])
  comb = combn(nrow(mindf[[h]]), 2)
  connected[[h]] = comb[,which(as.numeric(dist(data.frame(networks[[h]][k[h]])))<=Rc[[h]][k[h]])]
  connections[[h]] = data.frame(
    from = mindf[[h]][connected[[h]][1, ], 1:2],
    to = mindf[[h]][connected[[h]][2, ], 1:2]
    )
  names(connections[[h]]) = c("x1", "y1", "x2", "y2")
}

color = c("pink", "blue", "green")
title = c("Plots of the Mean Rc with size of 20", "Plots of the Mean Rc with size of 50", "Plots of the Mean Rc with size of 100")

for (h in 1:3){
  plot = 
    ggplot(mindf[[h]], aes(x = mindf[[h]]$x, y = mindf[[h]]$y)) + 
    geom_point(col = "black", size = 3) +
    geom_segment(data = connections[[h]], 
                 aes(x = x1, y = y1, xend = x2, yend = y2), col = color[h]) +
    labs(x = "X-coordinate", y = "Y-coordinate", title = title[h])
  print(plot)
}


```

Plots of Rc with the largest

```{r}

mindf = list()
connected = list()
connections = list()

for (h in 1:3){
  mindf[[h]] = data.frame(networks[[h]][l[h]])
  comb = combn(nrow(mindf[[h]]), 2)
  connected[[h]] = comb[,which(as.numeric(dist(data.frame(networks[[h]][l[h]])))<=Rc[[h]][l[h]])]
  connections[[h]] = data.frame(
    from = mindf[[h]][connected[[h]][1, ], 1:2],
    to = mindf[[h]][connected[[h]][2, ], 1:2]
    )
  names(connections[[h]]) = c("x1", "y1", "x2", "y2")
}

color = c("pink", "blue", "green")
title = c("Plots of the Largest Rc with size of 20", "Plots of the Largest Rc with size of 50", "Plots of the Largest Rc with size of 100")

for (h in 1:3){
  plot = 
    ggplot(mindf[[h]], aes(x = mindf[[h]]$x, y = mindf[[h]]$y)) + 
    geom_point(col = "black", size = 3) +
    geom_segment(data = connections[[h]], 
                 aes(x = x1, y = y1, xend = x2, yend = y2), col = color[h]) +
    labs(x = "X-coordinate", y = "Y-coordinate", title = title[h])
  print(plot)
}


```


